Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-04-24 lqg-strings.tex
minro wording change to justification below eqn(19)

In the following we parameterise the string with $\tau = t$ and $\frac{\partial X}{\partial \sigma} \cdot \frac{\partial X}{\partial t}$. The first condition is the most natural since it means that a line of constant $\tau$ is a string as seen by a inertial Lorentz observer, and the second condition is chosen because this parameterisation implies the string velocity coincides with the tranverse velocity, which is a natural dynamical variable of the string since by construction it is reparameterisation invariant, so it doesn't change even tho our action changes under reparameterisation. From this, we find that the new form for the conserved energy per infinitesimal piece of the string is the regular energy of the Nambu-Goto string times the correction factor
\begin{equation} \label{eqn:string-energy}
	E \diff \sigma = T \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \diff s ,
\end{equation}
and the form of the wave equation maintains its shape as in
\begin{equation} \label{eqn:corrected-NG-wave-equation}
	\mu _{eff} \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial}{\partial s} \left[ T_{eff} \frac{\partial \Vec{X}}{\partial s} \right] = 0 ,
\end{equation}
where the effective mass density and effective tension are given by
\begin{align}
	\mu _{eff} & = \mu \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \label{eqn:effective-mass}            \\
	T_{eff}    & = \frac{T}{\gamma _{v_{\perp}}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) . \label{eqn:effective-tension}
\end{align}

>>>>

In the following we parameterise the string with $\tau = t$ and $\frac{\partial X}{\partial \sigma} \cdot \frac{\partial X}{\partial t}$. The first condition is the most natural since it means that a line of constant $\tau$ is a string as seen by a inertial Lorentz observer, and the second condition is chosen such that the $\sigma$ parameter is parallel to the parameter $s$, which is the length along the string parameter and this implies the string velocity coincides with the tranverse velocity, which is a natural dynamical variable of the string since by construction it is reparameterisation invariant, so it doesn't change even tho our action changes under reparameterisation. From this, we find that the new form for the conserved energy per infinitesimal piece of the string is the regular energy of the Nambu-Goto string times the correction factor
\begin{equation} \label{eqn:string-energy}
	E \diff \sigma = T \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \diff s ,
\end{equation}
and the form of the wave equation maintains its shape as in
\begin{equation} \label{eqn:corrected-NG-wave-equation}
	\mu _{eff} \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial}{\partial s} \left[ T_{eff} \frac{\partial \Vec{X}}{\partial s} \right] = 0 ,
\end{equation}
where the effective mass density and effective tension are given by
\begin{align}
	\mu _{eff} & = \mu \gamma _{v_{\perp}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \label{eqn:effective-mass}            \\
	T_{eff}    & = \frac{T}{\gamma _{v_{\perp}}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) . \label{eqn:effective-tension}
\end{align}
